Honors Draft

### 2020-02-17 chapters/article-draft.tex
work from weekend

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Honors Draft},
            pdfauthor={Raven McKnight},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\section{Introduction}\label{introduction}

@@

\section{Background}\label{background}

\subsection{Metro Transit}\label{metro-transit}

@@

\subsection{Transit Market Areas}\label{transit-market-areas}

@@

\section{Data}\label{data}

\subsection{Metro Transit Data}\label{metro-transit-data}

@@

\subsubsection{Data Interpolation}\label{data-interpolation}

@@

\subsubsection{Data Aggregation}\label{data-aggregation}

@@

\subsection{Other data sources}\label{other-data-sources}

@@

\section{Models}\label{models}

\subsection{Stan}\label{stan}

@@

\subsection{Poisson Regression}\label{poisson-regression}

@@

\subsubsection{Model 1}\label{model-1}

@@

\subsection{Overdispersed Poisson
Regression}\label{overdispersed-poisson-regression}

@@

\subsubsection{Model 2}\label{model-2}

@@

@@

\subsection{Horseshoe Priors and Variable
Selection}\label{horseshoe-priors-and-variable-selection}

@@

\subsubsection{Spike and Slab - needs
graphics}\label{spike-and-slab---needs-graphics}

@@

\subsubsection{Horseshoe - needs
graphics}\label{horseshoe---needs-graphics}

@@

\subsubsection{Regularized Horseshoe - needs
graphics}\label{regularized-horseshoe---needs-graphics}

@@

\subsubsection{Model 3}\label{model-3}

For this study, we implement the regularize horseshoe using code
modified from Piironen \& Vehtari.

Notably, Model 3 experienced one divergent transition after warmup.
However, the model was fitted several times with no divergent
transitions. A ``false alarm'' divergent transition can occur when the
cutoff for determining a divergent transition is too low; this can be
true in the case of particularly complex posteriors. Because only 1 out
of 20,000 iterations produced a divergent transition, we can proceed
with caution using Model 3.

\subsection{Adding Spatial Structure}\label{adding-spatial-structure}

@@

\subsubsection{Conditional Autoregressive
Priors}\label{conditional-autoregressive-priors}

@@

\subsubsection{Intrinsic Conditional
Autoregressive}\label{intrinsic-conditional-autoregressive}

@@

\subsubsection{Besag-York-Mollie (BYM)}\label{besag-york-mollie-bym}

@@

\subsubsection{BYM2}\label{bym2}

@@

\subsubsection{Model 4}\label{model-4}

@@

\subsubsection{Model 5}\label{model-5}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \toprule
Parameter & Rhat & n\_eff & mean & sd & 2.5\% & 97.5\% \\ 
  \midrule
beta0 & 1.0 & 5837 & -1.9 & 0.0 & -1.9 & -1.8 \\ 
  sigma & 1.0 & 721 & 2.8 & 0.4 & 2.1 & 3.6 \\ 
  rho & 1.0 & 713 & 0.9 & 0.0 & 0.8 & 0.9 \\ 
  beta[1] & 1.0 & 3637 & -0.1 & 0.1 & -0.2 & -0.0 \\ 
  beta[2] & 1.0 & 8170 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
  beta[3] & 1.0 & 3987 & 0.0 & 0.0 & -0.0 & 0.1 \\ 
  beta[4] & 1.0 & 8531 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
  beta[5] & 1.0 & 7619 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
  beta[6] & 1.0 & 2999 & 0.2 & 0.1 & 0.1 & 0.3 \\ 
  beta[7] & 1.0 & 3726 & 0.0 & 0.0 & -0.0 & 0.1 \\ 
  beta[8] & 1.0 & 7956 & 0.0 & 0.0 & -0.0 & 0.1 \\ 
  beta[9] & 1.0 & 5622 & 0.0 & 0.0 & -0.0 & 0.1 \\ 
  beta[10] & 1.0 & 7530 & 0.1 & 0.0 & 0.1 & 0.2 \\ 
  beta[11] & 1.0 & 4558 & -0.1 & 0.0 & -0.1 & 0.0 \\ 
  beta[12] & 1.0 & 11150 & 0.0 & 0.0 & -0.0 & 0.0 \\ 
  beta[13] & 1.0 & 8289 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
  beta[14] & 1.0 & 5469 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
  beta[15] & 1.0 & 4822 & 0.1 & 0.0 & -0.0 & 0.1 \\ 
  beta[16] & 1.0 & 3863 & -0.1 & 0.0 & -0.1 & 0.0 \\ 
  beta[17] & 1.0 & 2094 & 0.1 & 0.0 & -0.0 & 0.1 \\ 
  beta[18] & 1.0 & 6949 & -0.0 & 0.0 & -0.1 & 0.0 \\ 
   \bottomrule
\end{tabular}
\caption{Stan output for Model 5} 
\end{table}

\section{Discussion}\label{discussion}

@@

\begin{itemize}
\tightlist
\item
  bymhrs is probably not ``worth it'', needs to be reparameterized/coded
  by someone better than me
\item
  incorporating overdispersion is the most important improvement in
  terms of model fit
\end{itemize}

\section{Appendix: Stan Code}\label{appendix-stan-code}

\subsection{Model 1}\label{model-1-1}

@@

\subsection{Model 2}\label{model-2-1}

@@

\subsection{Model 3}\label{model-3-1}

@@

\subsection{Model 4}\label{model-4-1}

The BYM2 model is fit using code from Morris et al.

@@

\subsection{Model 5}\label{model-5-1}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Honors Draft},
  pdfauthor={Raven McKnight},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{float}
\usepackage{booktabs}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{background}{%
\section{Background}\label{background}}

\hypertarget{metro-transit}{%
\subsection{Metro Transit}\label{metro-transit}}

@@

\hypertarget{transit-market-areas}{%
\subsection{Transit Market Areas}\label{transit-market-areas}}

@@

\hypertarget{data}{%
\section{Data}\label{data}}

\hypertarget{metro-transit-data}{%
\subsection{Metro Transit Data}\label{metro-transit-data}}

@@

\hypertarget{data-interpolation}{%
\subsubsection{Data Interpolation}\label{data-interpolation}}

@@

\hypertarget{data-aggregation}{%
\subsubsection{Data Aggregation}\label{data-aggregation}}

@@

\hypertarget{other-data-sources}{%
\subsection{Other data sources}\label{other-data-sources}}

@@

\hypertarget{models}{%
\section{Models}\label{models}}

\hypertarget{stan}{%
\subsection{Stan}\label{stan}}

@@

\hypertarget{poisson-regression}{%
\subsection{Poisson Regression}\label{poisson-regression}}

@@

\hypertarget{model-1}{%
\subsubsection{Model 1}\label{model-1}}

@@

\hypertarget{overdispersed-poisson-regression}{%
\subsection{Overdispersed Poisson
Regression}\label{overdispersed-poisson-regression}}

@@

\hypertarget{model-2}{%
\subsubsection{Model 2}\label{model-2}}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width = 6in]{ppcheckmod2.png}
  \caption{Posterior predictive check for Model 1.}
\end{figure}

@@

\hypertarget{horseshoe-priors-and-variable-selection}{%
\subsection{Horseshoe Priors and Variable
Selection}\label{horseshoe-priors-and-variable-selection}}

@@

\hypertarget{spike-and-slab---needs-graphics}{%
\subsubsection{Spike and Slab - needs
graphics}\label{spike-and-slab---needs-graphics}}

@@

\hypertarget{horseshoe---needs-graphics}{%
\subsubsection{Horseshoe - needs
graphics}\label{horseshoe---needs-graphics}}

@@

\hypertarget{regularized-horseshoe---needs-graphics}{%
\subsubsection{Regularized Horseshoe - needs
graphics}\label{regularized-horseshoe---needs-graphics}}

@@

\hypertarget{model-3}{%
\subsubsection{Model 3}\label{model-3}}

For this study, we implement the regularized horseshoe using code
modified from Piironen \& Vehtari.

Notably, Model 3 experienced one divergent transition after warmup.
However, the model was fitted several times with no divergent
transitions. A ``false alarm'' divergent transition can occur when the
cutoff for determining a divergent transition is too low; this can be
true in the case of particularly complex posteriors. Because only 1 out
of 20,000 iterations produced a divergent transition, we can proceed
with caution using Model 3. Additionally, the parameter estimates
provided by Model 3 closely match those from Models 1 and 2, suggesting
that the single divergent transition did not have an adverse effect on
the posterior estimates.

The posterior predictive checks for Model 3 match Model 2 almost
perfectly - this is to be expected. The addition of horseshoe priors on
\(\beta_k\) does not attempt to improve model fit, but to determine
which covariates are most ``important''.

On that note, we can see that Model 3 \emph{did} shrink two \(\beta_k\)
exactly to zero.

\hypertarget{adding-spatial-structure}{%
\subsection{Adding Spatial Structure}\label{adding-spatial-structure}}

@@

\hypertarget{conditional-autoregressive-priors}{%
\subsubsection{Conditional Autoregressive
Priors}\label{conditional-autoregressive-priors}}

@@

\hypertarget{intrinsic-conditional-autoregressive}{%
\subsubsection{Intrinsic Conditional
Autoregressive}\label{intrinsic-conditional-autoregressive}}

@@

\hypertarget{besag-york-mollie-bym}{%
\subsubsection{Besag-York-Mollie (BYM)}\label{besag-york-mollie-bym}}

@@

\hypertarget{bym2}{%
\subsubsection{BYM2}\label{bym2}}

@@

\hypertarget{model-4}{%
\subsubsection{Model 4}\label{model-4}}

@@

\hypertarget{model-5}{%
\subsubsection{Model 5}\label{model-5}}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrrr}
  \toprule
Parameter & Rhat & n\_eff & mean & sd & 2.5\% & 97.5\% \\ 
  \midrule
beta0 & 1.000 & 5837 & -1.878 & 0.028 & -1.934 & -1.822 \\ 
  sigma & 1.010 &  721 & 2.826 & 0.359 & 2.138 & 3.561 \\ 
  theta[5] & 1.000 & 19566 & -0.188 & 0.787 & -1.722 & 1.349 \\ 
  rho & 1.012 &  713 & 0.900 & 0.031 & 0.824 & 0.946 \\ 
  phi[5] & 1.004 & 1652 & 5.974 & 1.573 & 3.264 & 9.527 \\ 
  beta[1] & 1.001 & 3637 & -0.119 & 0.059 & -0.233 & -0.002 \\ 
  beta[2] & 1.001 & 8170 & -0.005 & 0.027 & -0.069 & 0.049 \\ 
  beta[3] & 1.000 & 3987 & 0.024 & 0.030 & -0.019 & 0.096 \\ 
  beta[4] & 1.000 & 8531 & -0.004 & 0.022 & -0.057 & 0.040 \\ 
  beta[5] & 1.000 & 7619 & -0.012 & 0.026 & -0.076 & 0.030 \\ 
  beta[6] & 1.001 & 2999 & 0.164 & 0.055 & 0.051 & 0.268 \\ 
  beta[7] & 1.000 & 3726 & 0.032 & 0.035 & -0.016 & 0.114 \\ 
  beta[8] & 1.000 & 7956 & 0.010 & 0.025 & -0.032 & 0.074 \\ 
  beta[9] & 1.000 & 5622 & 0.019 & 0.028 & -0.023 & 0.089 \\ 
  beta[10] & 1.000 & 7530 & 0.144 & 0.033 & 0.079 & 0.208 \\ 
  beta[11] & 1.000 & 4558 & -0.057 & 0.034 & -0.123 & 0.001 \\ 
  beta[12] & 1.000 & 11150 & 0.004 & 0.018 & -0.031 & 0.046 \\ 
  beta[13] & 1.000 & 8289 & -0.017 & 0.024 & -0.073 & 0.020 \\ 
  beta[14] & 1.000 & 5469 & -0.028 & 0.031 & -0.100 & 0.015 \\ 
  beta[15] & 1.000 & 4822 & 0.060 & 0.035 & -0.001 & 0.130 \\ 
  beta[16] & 1.001 & 3863 & -0.060 & 0.038 & -0.134 & 0.003 \\ 
  beta[17] & 1.000 & 2094 & 0.051 & 0.041 & -0.008 & 0.137 \\ 
  beta[18] & 1.000 & 6949 & -0.010 & 0.021 & -0.061 & 0.026 \\ 
   \bottomrule
\end{tabular}
\caption{Stan output for Model 5} 
\end{table}

The posterior predictive checks and mapped residuals for Model 5 are
very similar to those for Model 4. Like Model 2, the slow sampling time
is largely caused by autocorrelation between iterations.

The more interesting comparison here is with Model 3. The horseshoe
priors in Model 5 fail to shrink any parameters \emph{exactly} to zero.
As previously discussed, running the model for more iterations would
likely cuase the coverage intervals on the \(\beta_k\) estimates to
tighten.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

While the most complex model \emph{does} converge and provide reasonable
parameter estimates, its computational inefficiency may not be worth the
addition of horseshoe priors to the BYM2 model, depending on the
application. A more efficient approach may be to conduct variable
selection using horseshoe priors on a simpler model (in our case, Model
1 or Model 3, for example) before incorporating the ICAR component.

\hypertarget{appendix-stan-code}{%
\section{Appendix: Stan Code}\label{appendix-stan-code}}

\hypertarget{model-1-1}{%
\subsection{Model 1}\label{model-1-1}}

@@

\hypertarget{model-2-1}{%
\subsection{Model 2}\label{model-2-1}}

@@

\hypertarget{model-3-1}{%
\subsection{Model 3}\label{model-3-1}}

@@

\hypertarget{model-4-1}{%
\subsection{Model 4}\label{model-4-1}}

The BYM2 model is fit using code from Morris et al.~

@@

\hypertarget{model-5-1}{%
\subsection{Model 5}\label{model-5-1}}
